Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-01-26 summary_minh_edited.tex
updated response to 14

However, because we do not observe $P$ but rather only the noisy
adjacency matrix $A \sim \BG(P)$, the natural approach then is
to perform SSC on the rows of the spectral embedding of \(A\), 
since they will still lie approximately on the $K$ subspaces 
\citep{rubindelanchy2017statistical}. 
We will show in Theorem~\ref{theorem5} that, with probability converging to
one as $n \rightarrow \infty$, the rows of the ASE of $A$ also
satisfy the subspace detection property. 
Theorem~\ref{theorem5} builds upon existing work by
\citet{rubindelanchy2017statistical} who describe the convergence
behavior of the ASE of \(A\) to that of \(\tilde{\Pi} XU\), and
\citet{jmlr-v28-wang13} who show the necessary conditions for the
subspace detection property to hold in noisy cases where the points lie
near subspaces. Finally we emphasize that while
\citet{noroozi2019estimation} also considered the use of SSC for
community recovery in PABM, they instead applied SSC to the rows of
\(A\) itself, foregoing
the embedding step altogether. It is however much harder to show that
the rows of $A$ satisfy the subspace detection property and thus, to
the best of our knowledge, there is currently no consistency result
regarding the application of SSC to the rows of $A$.

>>>>

However, because we do not observe $P$ but rather only the noisy
adjacency matrix $A \sim \BG(P)$, the natural approach then is
to perform SSC on the rows of the spectral embedding of $A$, 
since the embedding of $P$ consists of $K$ subspaces (Theorem~\ref{theorem2}), 
and so the embedding of $A$ will lie approximately on the $K$ subspaces. 
We will show in Theorem~\ref{theorem5} that, with probability converging to
one as $n \rightarrow \infty$, the rows of the ASE of $A$ also
satisfy the subspace detection property. 
Theorem~\ref{theorem5} builds upon existing work by
\citet{rubindelanchy2017statistical} who describe the convergence
behavior of the ASE of \(A\) to that of \(\tilde{\Pi} XU\), and
\citet{jmlr-v28-wang13} who show the necessary conditions for the
subspace detection property to hold in noisy cases where the points lie
near subspaces. Finally we emphasize that while
\citet{noroozi2019estimation} also considered the use of SSC for
community recovery in PABM, they instead applied SSC to the rows of
\(A\) itself, foregoing
the embedding step altogether. It is however much harder to show that
the rows of $A$ satisfy the subspace detection property and thus, to
the best of our knowledge, there is currently no consistency result
regarding the application of SSC to the rows of $A$.
